Simulating High-Dimensional Multivariate Data

### 2020-12-11 030-bigsimr-package.Rmd
4th draft. fix mle of log normal var

```{r ch030-aq-ozone-pars, echo=TRUE}
mle_mean <- function(x) mean(log(x))
mle_sd <- function(x) mean( (log(x) - mean(log(x)))^2 )

@@

```{r ch030-margins-alist, echo=TRUE}
margins <- alist(
    qnorm(mean = 77.871, sd = 9.4855),
    qlnorm(meanlog = 3.419, sdlog = 0.7426),
)
```

@@

```{r ch030-cor-bounds-pearson, echo=TRUE}
cor_bounds(margins = margins, type = 'pearson')
```

>>>>

```{r ch030-aq-ozone-pars, echo=TRUE}
mle_mean <- function(x) mean(log(x))
mle_sd <- function(x) mean( sqrt( (log(x) - mean(log(x)))^2 ) )

@@

```{r ch030-margins-alist, echo=TRUE}
margins <- alist(
    qnorm(mean = 77.871, sd = 9.4855),
    qlnorm(meanlog = 3.419, sdlog = 0.6967),
)
```

@@

```{r ch030-cor-bounds-pearson, echo=TRUE}
cor_bounds(margins = margins, type = 'pearson', reps=1e6)
```
